### 2018-06-29 ms.tex
Add some figures  for placeholders.

The prevalence survey data were extracted from the MAP prevalence survey database [@].
As the prevalence surveys cover different are ranges they were standardisePars using the model from [@].

@@

\begin{figure}[!h]
% to be removed before submission
\includegraphics{figures/mdg_points_and_polygons.png}
\caption{{\bf Bold the figure title.}
Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
\label{fig1}
\end{figure}

>>>>

The prevalence survey data were extracted from the MAP prevalence survey database [@].
As the prevalence surveys cover different are ranges they were standardised using the model from [@].

@@

\begin{figure}[!h]
% to be removed before submission
\includegraphics[width = 0.9\textwidth]{figures/mdg_points_and_polygons.png}
\caption{{\bf Madagascar polygon data and predictions from the combined model.}
Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
\label{fig1}
\end{figure}

\begin{figure}[!h]
% to be removed before submission
\includegraphics[width = 0.9\textwidth]{figures/pred_obs_map.png}
\caption{{\bf Indonesia polygon data and predictions from the combined model.}
Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
\label{fig1}
\end{figure}
